A Transactional Memory System for Parallel Python

### 2014-06-06 talk/dls2014/paper/paper.tex
fix references

\bibitem{harris10} Harris, Tim, James Larus, and Ravi
  Rajwar. "Transactional memory." \emph{Synthesis Lectures on Computer
  Architecture 5.1} (2010): 1-263.

\bibitem{guerraoui08} Guerraoui, Rachid, and Michal Kapalka. "On the
  correctness of transactional memory." \emph{Proceedings of the 13th
    ACM SIGPLAN Symposium on Principles and practice of parallel
    programming.} ACM, 2008.

\bibitem{blundell06} Blundell, Colin, E. Christopher Lewis, and Milo
  Martin. "Unrestricted transactional memory: Supporting I/O and system
  calls within transactions." (2006).
\bibitem{spear08} Spear, Michael F., et al. "Implementing and
  exploiting inevitability in software transactional memory."
  \emph{Parallel Processing, 2008}. ICPP'08. 37th International
  Conference on. IEEE, 2008.

@@

\bibitem{rajwar05} Rajwar, Ravi, Maurice Herlihy, and Konrad
  Lai. "Virtualizing transactional memory." \emph{Computer
    Architecture}, 2005. ISCA'05. Proceedings. 32nd International
  Symposium on. IEEE, 2005.

\bibitem{chung06} Chung, JaeWoong, et al. "Tradeoffs in transactional
  memory virtualization." \emph{ACM SIGARCH Computer Architecture
  News}. Vol. 34. No. 5. ACM, 2006.

\bibitem{martin09} Martín Abadi, Tim Harris, and Mojtaba
  Mehrara. 2009. Transactional memory with strong atomicity using
  off-the-shelf memory protection hardware. SIGPLAN Not. 44, 4 (February
  2009), 185-196.

@@

\bibitem{odaira14}
  Odaira, Rei, Jose G. Castanos, and Hisanobu Tomari.  "Eliminating
  global interpreter locks in Ruby through hardware transactional
  memory."  \emph{Proceedings of the 19th ACM SIGPLAN symposium on
    Principles and practice of parallel programming.} ACM, 2014.

\bibitem{warmhoff13}
  Wamhoff, Jons-Tobias, et al. "FastLane: improving performance of
  software transactional memory for low thread counts."
  \emph{Proceedings of the 18th ACM SIGPLAN symposium on Principles
    and practice of parallel programming.} ACM, 2013.

\bibitem{drago11}
  Dragojević, Aleksandar, et al. "Why STM can be more than a research
  toy." \emph{Communications of the ACM} 54.4 (2011): 70-77.

\bibitem{cascaval08}
  Cascaval, Calin, et al. "Software transactional memory: Why is it
  only a research toy?." \emph{Queue} 6.5 (2008): 40.

\bibitem{nicholas06}
  Nicholas Riley and Craig Zilles. 2006. Hardware transactional memory
  support for lightweight dynamic language evolution. \emph{In
    Companion to the 21st ACM SIGPLAN symposium on Object-oriented
    programming systems, languages, and applications} (OOPSLA
  '06). ACM, New York, NY, USA

\bibitem{fuad10}
  Fuad Tabba. 2010. Adding concurrency in python using a commercial
  processor's hardware transactional memory support. \emph{SIGARCH
  Comput. Archit. News 38}, 5 (April 2010)

\bibitem{felber07}
  Felber, Pascal, et al. "Transactifying applications using an open
  compiler framework." \emph{TRANSACT}, August (2007): 4-6.

@@

\bibitem{spear09}
  Spear, Michael F., et al. "Transactional mutex locks." \emph{SIGPLAN
    Workshop on Transactional Computing.} 2009.

\bibitem{lamport79}
  Lamport, Leslie. "How to make a multiprocessor computer that
  correctly executes multiprocess programs." \emph{Computers, IEEE
    Transactions} on 100.9 (1979): 690-691.

\bibitem{victor11}
  Victor Pankratius and Ali-Reza Adl-Tabatabai. 2011. A study of
  transactional memory vs. locks in practice. In \emph{Proceedings of
    the twenty-third annual ACM symposium on Parallelism in algorithms
    and architectures} (SPAA '11). ACM, New York, NY, USA

@@

\bibitem{tim03}
  Tim Harris and Keir Fraser. 2003. Language support for lightweight
  transactions. \emph{In Proceedings of the 18th annual ACM SIGPLAN
    conference on Object-oriented programing, systems, languages, and
    applications} (OOPSLA '03).

\bibitem{tim05}
  Tim Harris, Simon Marlow, Simon Peyton-Jones, and Maurice
  Herlihy. 2005. Composable memory transactions. \emph{In Proceedings
    of the tenth ACM SIGPLAN symposium on Principles and practice of
    parallel programming} (PPoPP '05).

>>>>

\bibitem{harris10} Harris, Tim, James Larus, and Ravi
  Rajwar. "Transactional memory." \emph{Synthesis Lectures on Computer
  Architecture 5.1} (2010)

\bibitem{guerraoui08}
  Rachid Guerraoui and Michal Kapalka. 2008. On the correctness of
  transactional memory. In \emph{Proceedings of the 13th ACM SIGPLAN
    Symposium on Principles and practice of parallel programming} (PPoPP
  '08).

\bibitem{blundell06} Blundell, Colin, E. Christopher Lewis, and Milo
  Martin. "Unrestricted transactional memory: Supporting I/O and system
  calls within transactions." (2006).

\bibitem{spear08} Michael F. Spear and Michael Silverman and Luke
  Daless and Maged M. Michael and Michael L. Scott. 2008. "Implementing
  and exploiting inevitability in software transactional memory."  In
  \emph{Proc. 37th IEEE international conference on parallel
    processing} (ICPP '08), 59-66

@@

\bibitem{rajwar05} Ravi Rajwar, Maurice Herlihy, and Konrad
  Lai. 2005. Virtualizing Transactional Memory. In \emph{Proceedings of
    the 32nd annual international symposium on Computer Architecture}
  (ISCA '05).

\bibitem{chung06} JaeWoong Chung, Chi Cao Minh, Austen McDonald,
  Travis Skare, Hassan Chafi, Brian D. Carlstrom, Christos Kozyrakis,
  and Kunle Olukotun. 2006. Tradeoffs in transactional memory
  virtualization. \emph{SIGOPS Oper. Syst. Rev.} 40, 5 (October 2006),
  371-381.

\bibitem{martin09} Martín Abadi, Tim Harris, and Mojtaba
  Mehrara. 2009. Transactional memory with strong atomicity using
  off-the-shelf memory protection hardware. \emph{SIGPLAN Not.} 44, 4
  (February 2009), 185-196.

@@

\bibitem{odaira14}
  Rei Odaira, Jose G. Castanos, and Hisanobu Tomari. 2014. Eliminating
  global interpreter locks in ruby through hardware transactional
  memory. In \emph{Proceedings of the 19th ACM SIGPLAN symposium on
    Principles and practice of parallel programming} (PPoPP '14).

\bibitem{warmhoff13}
  Jons-Tobias Wamhoff, Christof Fetzer, Pascal Felber, Etienne Rivière,
  and Gilles Muller. 2013. FastLane: improving performance of software
  transactional memory for low thread counts. \emph{SIGPLAN Not.} 48, 8
  (February 2013), 113-122.

\bibitem{drago11} Aleksandar Dragojević, Pascal Felber, Vincent
  Gramoli, and Rachid Guerraoui. 2011. Why STM can be more than a
  research toy. \emph{Commun. ACM} 54, 4 (April 2011), 70-77.

\bibitem{cascaval08}
  Calin Cascaval, Colin Blundell, Maged Michael, Harold W. Cain, Peng
  Wu, Stefanie Chiras, and Siddhartha Chatterjee. 2008. Software
  transactional memory: why is it only a research
  toy?. \emph{Commun. ACM} 51, 11 (November 2008), 40-46.

\bibitem{nicholas06}
  Nicholas Riley and Craig Zilles. 2006. Hardware transactional memory
  support for lightweight dynamic language evolution. \emph{In
    Companion to the 21st ACM SIGPLAN symposium on Object-oriented
    programming systems, languages, and applications} (OOPSLA
  '06).

\bibitem{fuad10}
  Fuad Tabba. 2010. Adding concurrency in python using a commercial
  processor's hardware transactional memory support. \emph{SIGARCH
  Comput. Archit. News 38}, 5 (April 2010), 12-19.

\bibitem{felber07}
  Pascal Felber and Torvald Riegel and Christof Fetzer and Martin
  Süßkraut and Ulrich Müller and Heiko Sturzrehm. 2007. Transactifying
  applications using an open compiler framework. \emph{TRANSACT}, August
  (2007): 4-6.

@@

\bibitem{spear09}
  Luke Dalessandro, Dave Dice, Michael Scott, Nir Shavit, and Michael
  Spear. 2010. Transactional mutex locks. In \emph{Proceedings of the
    16th international Euro-Par conference on Parallel processing: Part
    II} (Euro-Par'10), Pasqua D'Ambra, Mario Guarracino, and Domenico
  Talia (Eds.). Springer-Verlag, Berlin, Heidelberg, 2-13.

\bibitem{lamport79}
  L. Lamport. 1979. How to Make a Multiprocessor Computer That Correctly
  Executes Multiprocess Programs. \emph{IEEE Trans. Comput.} 28, 9
  (September 1979), 690-691.

\bibitem{victor11}
  Victor Pankratius and Ali-Reza Adl-Tabatabai. 2011. A study of
  transactional memory vs. locks in practice. In \emph{Proceedings of
    the twenty-third annual ACM symposium on Parallelism in algorithms
    and architectures} (SPAA '11).

@@

\bibitem{tim03}
  Tim Harris and Keir Fraser. 2003. Language support for lightweight
  transactions. \emph{In Proceedings of the 18th annual ACM SIGPLAN
    conference on Object-oriented programing, systems, languages, and
    applications} (OOPSLA '03), 388-402.

\bibitem{tim05} Tim Harris, Simon Marlow, Simon Peyton Jones, and
  Maurice Herlihy. 2008. Composable memory transactions.
  \emph{Commun. ACM} 51, 8 (August 2008), 91-100.
